The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-19 document/ms.tex
tdm edit box paragraph

Since the search procedure described here was tuned to discover transit
signals, we do not consider the distribution or potential astrophysical nature
of any models besides the \modelname{transit} model.
In the future, it would be interesting to relax this goal and investigate the
other model classes because, for example, the \modelname{box} model is
probably sensitive to other astrophysical phenomena like secondary eclipses.
In a cursory investigation it is clear that the majority of signals labeled
\modelname{box} in our analysis are noise but a subset are likely to be
astrophysical in nature.

>>>>

Since the search procedure described here was tuned to discover transit
signals, we do not consider the distribution or potential astrophysical nature
of any models besides the \modelname{transit} model.
In the future, it would be interesting to relax this goal and investigate the
other model classes.  In particular, the \modelname{box} model is
sensitive to astrophysical phenomena, notably occultations of white dwarfs,
which produce a perfect box-shaped signal.  In a cursory investigation 
it is clear that the majority of signals labeled
\modelname{box} in our analysis are noise; however, a subset are likely to be
astrophysical in nature.
